---
title: "Building Materials"
author: "Xiaochi"
date: "24/02/2020"
output: html_document
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = TRUE,
	warning = TRUE
)
library(tidyverse)
library(ggpubr)
library(knitr)
library(rstatix)
library(scales)
theme_set(theme_bw())
```

# Trace element concentration ~ Building material

```{r}
df_newly_cleaned <- read_rds("../data_output/df_vege.rds")

df_newly_cleaned %>% 
  count(matirial_all, sort = TRUE)

material_levels = c("brick", "timber", "fibro", "metal", "stone")

df_matirial_test <- df_newly_cleaned %>% 
  mutate(matirial_all = factor(matirial_all, levels = material_levels)) %>%
  filter(matirial_all != "unknown")

df_test <- df_newly_cleaned %>% 
  mutate(matirial_all = factor(matirial_all, levels = material_levels))

df_test %>% 
  count(matirial_all)

df_matirial_test %>% 
  count(matirial_all)
```

## Pb

```{r eval=FALSE}
df_matirial_test %>% 
  group_by(matirial_all) %>% 
  get_summary_stats(Pb, type = "common")
```


```{r}
ggline(df_matirial_test, 
       x = "matirial_all", 
       y = "Pb", 
       add = c("mean_ci"), 
       xlab = "Building Material",
       font.tickslab = 12,
       ylab = "Pb Concentration (mg/kg)",
       title = "Mean Plot with 95% CI")
```

```{r}
res.kruskal <- df_matirial_test %>% 
  kruskal_test(Pb ~ matirial_all)
res.kruskal
```

Since the p-value < 0.001, we can conclude that there are significant differences between Pb concentrations in different location groups.

```{r}
effect_size <- df_matirial_test %>% 
  kruskal_effsize(Pb ~ matirial_all)
effect_size
```

We could also get the effect size of the Kruskal-Wallis test.
The interpretation values commonly in published literature are: 0.01 -- 0.06 (small effect), 0.06 -- 0.14 (moderate effect) and >= 0.14 (large effect).
Therefore, a samll effect was detected.

From the output of the Kruskal-Wallis test, we know that there is a significant difference between groups, but we don’t know which pairs of groups are different.
A significant Kruskal-Wallis test is generally followed up by Dunn’s test to identify which groups are different. 

```{r}
pwc <-  df_matirial_test %>% 
  dunn_test(Pb ~ matirial_all, p.adjust.method = "bonferroni")
pwc
```



```{r}
mean_fun <- function(x){
  return(data.frame(y = mean(x),
                    label = format(round(mean(x, na.rm = TRUE), 1), nsmall = 1)
                    )
         )
}
```



```{r boxplot}
n_fun <- function(x){
  return(data.frame(y = median(x) + 30, 
                    label = str_c("n = ", length(x))))
}

Pb_material <- df_matirial_test %>% 
  ggplot(aes(x = matirial_all, y = Pb, 
             color = matirial_all)) +
  stat_boxplot(geom = "errorbar", width = 0.2) +
  geom_boxplot(outlier.shape = NA) +
  # stat_summary(fun.data = n_fun, geom = "text") +
  stat_pvalue_manual(pwc, 
                     hide.ns = TRUE, 
                     remove.bracket = FALSE, tip.length = 0.001, 
                     y.position = 780, step.increase = 0.005,
                     #label = "p = {scientific(p.adj, 2)}", label.size = 3
                     ) +
  # add the number of observations
  stat_summary(fun.data = n_fun, geom = "text", colour = "black") +
  # add mean point
  stat_summary(fun = mean, geom = "point", shape = 20, size = 5) +
  # add mean text
  stat_summary(fun.data = mean_fun, geom = "text", colour = "black",  
               position = position_nudge(x = 0.22)) +
  labs(x = "Building Material",
       y="Pb Concentration (mg/kg)",
       subtitle = get_test_label(res.kruskal, detailed = TRUE),
       caption = get_pwc_label(pwc)) +
  scale_y_continuous(#limits = quantile(df_newly_cleaned$Pb, c(0, 1)),
                     breaks = seq(0, 1100, by = 100))+
  coord_cartesian(ylim = c(0, 1100)) +
  theme(panel.border = element_blank(), 
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), 
        axis.line = element_line(colour = "black"),
        axis.text = element_text(colour = "black"),
        text=element_text(family="Helvetica"),
        legend.position = "none")

Pb_material
```


```{r boxplot}
ggsave("../fig_output/Material/Pb.png", Pb_material, width = 7, height = 5)
```


```{r}
df_matirial_test %>% 
  group_by(matirial_all) %>% 
  summarise(ci = list(mean_cl_boot(Pb))) %>% 
  unnest(cols = c(ci))
```


## As

```{r eval=FALSE}
df_matirial_test %>% 
  group_by(matirial_all) %>% 
  get_summary_stats(As, type = "common")
```


```{r}
ggline(df_matirial_test, 
       x = "matirial_all", 
       y = "As", 
       add = c("mean_ci"), 
       xlab = "Building Material",
       font.tickslab = 12,
       ylab = "As Concentration (mg/kg)",
       title = "Mean Plot with 95% CI")
```

```{r}
res.kruskal <- df_matirial_test %>% 
  kruskal_test(As ~ matirial_all)
res.kruskal
```

```{r}
effect_size <- df_matirial_test %>% 
  kruskal_effsize(As ~ matirial_all)
effect_size
```

```{r}
pwc <-  df_matirial_test %>% 
  dunn_test(As ~ matirial_all, p.adjust.method = "bonferroni")
pwc
```


```{r boxplot}
n_fun <- function(x){
  return(data.frame(y = median(x) - 2, 
                    label = str_c("n = ", length(x))))
}

As_material <- df_matirial_test %>% 
  ggplot(aes(x = matirial_all, y = As, 
             color = matirial_all)) +
  stat_boxplot(geom = "errorbar", width = 0.2) +
  geom_boxplot(outlier.shape = NA) +
  # stat_summary(fun.data = n_fun, geom = "text") +
  stat_pvalue_manual(pwc, 
                     hide.ns = TRUE, 
                     remove.bracket = FALSE, tip.length = 0.0002,
                     y.position = 40, step.increase = 0.001,
                     #label = "p = {scientific(p.adj, 2)}", label.size = 3
                     ) +
  # add the number of observations
  stat_summary(fun.data = n_fun, geom = "text", colour = "black") +
  # add mean point
  stat_summary(fun = mean, geom = "point", shape = 20, size = 5) +
  # add mean text
  stat_summary(fun.data = mean_fun, geom = "text", colour = "black",  
               position = position_nudge(x = 0.22)) +
  labs(x = "Building Material",
       y="As Concentration (mg/kg)",
       subtitle = get_test_label(res.kruskal, detailed = TRUE),
       caption = get_pwc_label(pwc)) +
  scale_y_continuous(# limits = quantile(df_newly_cleaned$As, c(0, 1)),
                     breaks = seq(0, 52, by = 10))+
  coord_cartesian(ylim = c(0, 50)) +
  theme(panel.border = element_blank(), 
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), 
        axis.line = element_line(colour = "black"),
        axis.text = element_text(colour = "black"),
        text=element_text(family="Helvetica"),
        legend.position = "none")
As_material
```


```{r boxplot}
ggsave("../fig_output/Material/As.png", As_material, width = 7, height = 5)
```


## Cr

```{r eval=FALSE}
df_matirial_test %>% 
  group_by(matirial_all) %>% 
  get_summary_stats(Cr, type = "common")
```


```{r}
ggline(df_matirial_test, 
       x = "matirial_all", 
       y = "Cr", 
       add = c("mean_ci"), 
       xlab = "Building Material",
       font.tickslab = 12,
       ylab = "Cr Concentration (mg/kg)",
       title = "Mean Plot with 95% CI")
```

```{r}
res.kruskal <- df_matirial_test %>% 
  kruskal_test(Cr ~ matirial_all)
res.kruskal
```

```{r}
effect_size <- df_matirial_test %>% 
  kruskal_effsize(Cr ~ matirial_all)
effect_size
```

```{r}
pwc <-  df_matirial_test %>% 
  dunn_test(Cr ~ matirial_all, p.adjust.method = "bonferroni")
pwc
```


```{r}
n_fun <- function(x){
  return(data.frame(y = median(x) - 5, 
                    label = str_c("n = ", length(x))))
}

Cr_material <- df_matirial_test %>% 
  ggplot(aes(x = matirial_all, y = Cr, 
             color = matirial_all)) +
  stat_boxplot(geom = "errorbar", width = 0.2) +
  geom_boxplot(outlier.shape = NA) +
  # stat_summary(fun.data = n_fun, geom = "text") +
  stat_pvalue_manual(pwc, 
                     hide.ns = TRUE, 
                     remove.bracket = FALSE, tip.length = 0.0003,
                     y.position = 110, step.increase = 0.0015,
                     #label = "p = {scientific(p.adj, 2)}", label.size = 3
                     ) +
  # add the number of observations
  stat_summary(fun.data = n_fun, geom = "text", colour = "black") +
  # add mean point
  stat_summary(fun = mean, geom = "point", shape = 20, size = 5) +
  # add mean text
  stat_summary(fun.data = mean_fun, geom = "text", colour = "black",  
               position = position_nudge(x = 0.22)) +
  labs(x = "Building Material",
       y="Cr Concentration (mg/kg)",
       subtitle = get_test_label(res.kruskal, detailed = TRUE),
       caption = get_pwc_label(pwc)) +
  scale_y_continuous(# limits = quantile(df_newly_cleaned$Cr, c(0, 1)),
                     breaks = seq(0, 140, by = 20))+
  coord_cartesian(ylim = c(0, 140)) +
  theme(panel.border = element_blank(), 
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), 
        axis.line = element_line(colour = "black"),
        axis.text = element_text(colour = "black"),
        text=element_text(family="Helvetica"),
        legend.position = "none")
Cr_material
```


```{r}
ggsave("../fig_output/Material/Cr.png", Cr_material, width = 7, height = 5)
```


## Cu

```{r}
ggline(df_matirial_test, 
       x = "matirial_all", 
       y = "Cu", 
       add = c("mean_ci"), 
       xlab = "Building Material",
       font.tickslab = 12,
       ylab = "Cu Concentration (mg/kg)",
       title = "Mean Plot with 95% CI")
```

```{r}
res.kruskal <- df_matirial_test %>% 
  kruskal_test(Cu ~ matirial_all)
res.kruskal
```

```{r}
effect_size <- df_matirial_test %>% 
  kruskal_effsize(Cu ~ matirial_all)
effect_size
```


```{r}
pwc <-  df_matirial_test %>% 
  dunn_test(Cu ~ matirial_all, p.adjust.method = "bonferroni")
pwc
```


```{r}
n_fun <- function(x){
  return(data.frame(y = median(x) - 5, 
                    label = str_c("n = ", length(x))))
}

Cu_material <- df_matirial_test %>% 
  ggplot(aes(x = matirial_all, y = Cu, 
             color = matirial_all)) +
  stat_boxplot(geom = "errorbar", width = 0.2) +
  geom_boxplot(outlier.shape = NA) +
  # stat_summary(fun.data = n_fun, geom = "text") +
  stat_pvalue_manual(pwc, 
                     hide.ns = TRUE, 
                     remove.bracket = FALSE, tip.length = 0.0003,
                     y.position = 120, step.increase = 0.0013,
                     #label = "p = {scientific(p.adj, 2)}", label.size = 3
                     ) +
  # add the number of observations
  stat_summary(fun.data = n_fun, geom = "text", colour = "black") +
  # add mean point
  stat_summary(fun = mean, geom = "point", shape = 20, size = 5) +
  # add mean text
  stat_summary(fun.data = mean_fun, geom = "text", colour = "black",  
               position = position_nudge(x = 0.22)) +
  labs(x = "Building Material",
       y="Cu Concentration (mg/kg)",
       subtitle = get_test_label(res.kruskal, detailed = TRUE),
       caption = get_pwc_label(pwc)) +
  scale_y_continuous(# limits = quantile(df_newly_cleaned$Cu, c(0, 1)),
                     breaks = seq(0, 190, by = 20))+
  coord_cartesian(ylim = c(0, 190)) +
  theme(panel.border = element_blank(), 
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), 
        axis.line = element_line(colour = "black"),
        axis.text = element_text(colour = "black"),
        text=element_text(family="Helvetica"),
        legend.position = "none")
Cu_material
```


```{r}
ggsave("../fig_output/Material/Cu.png", Cu_material, width = 7, height = 5)
```

## Mn

```{r}
ggline(df_matirial_test, 
       x = "matirial_all", 
       y = "Mn", 
       add = c("mean_ci"), 
       xlab = "Building Material",
       font.tickslab = 12,
       ylab = "Mn Concentration (mg/kg)",
       title = "Mean Plot with 95% CI")
```

```{r}
res.kruskal <- df_matirial_test %>% 
  kruskal_test(Mn ~ matirial_all)
res.kruskal
```

```{r}
effect_size <- df_matirial_test %>% 
  kruskal_effsize(Mn ~ matirial_all)
effect_size
```


```{r}
pwc <-  df_matirial_test %>% 
  dunn_test(Mn ~ matirial_all, p.adjust.method = "bonferroni")
pwc
```



```{r}
n_fun <- function(x){
  return(data.frame(y = median(x) - 35, 
                    label = str_c("n = ", length(x))))
}

Mn_material <- df_matirial_test %>% 
  ggplot(aes(x = matirial_all, y = Mn, 
             color = matirial_all)) +
  stat_boxplot(geom = "errorbar", width = 0.2) +
  geom_boxplot(outlier.shape = NA) +
  # stat_summary(fun.data = n_fun, geom = "text") +
  stat_pvalue_manual(pwc, 
                     hide.ns = TRUE, 
                     remove.bracket = FALSE, tip.length = 0.0008,
                     y.position = 1600, step.increase = 0.005,
                     #label = "p = {scientific(p.adj, 2)}", label.size = 3
                     ) +
  # add the number of observations
  stat_summary(fun.data = n_fun, geom = "text", colour = "black") +
  # add mean point
  stat_summary(fun = mean, geom = "point", shape = 20, size = 5) +
  # add mean text
  stat_summary(fun.data = mean_fun, geom = "text", colour = "black",  
               position = position_nudge(x = 0.22)) +
  labs(x = "Building Material",
       y="Mn Concentration (mg/kg)",
       subtitle = get_test_label(res.kruskal, detailed = TRUE),
       caption = get_pwc_label(pwc)) +
  scale_y_continuous(# limits = quantile(df_newly_cleaned$Mn, c(0, 1)),
                     breaks = seq(0, 2200, by = 200))+
  coord_cartesian(ylim = c(0, 2200)) +
  theme(panel.border = element_blank(), 
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), 
        axis.line = element_line(colour = "black"),
        axis.text = element_text(colour = "black"),
        text=element_text(family="Helvetica"),
        legend.position = "none")
Mn_material
```


```{r}
ggsave("../fig_output/Material/Mn.png", Mn_material, width = 7, height = 5)
```



## Ni

```{r}
ggline(df_matirial_test, 
       x = "matirial_all", 
       y = "Ni", 
       add = c("mean_ci"), 
       xlab = "Building Material",
       font.tickslab = 12,
       ylab = "Ni Concentration (mg/kg)",
       title = "Mean Plot with 95% CI")
```

```{r}
res.kruskal <- df_matirial_test %>% 
  kruskal_test(Ni ~ matirial_all)
res.kruskal
```

```{r}
effect_size <- df_matirial_test %>% 
  kruskal_effsize(Ni ~ matirial_all)
effect_size
```

```{r}
pwc <-  df_matirial_test %>% 
  dunn_test(Ni ~ matirial_all, p.adjust.method = "bonferroni")
pwc
```



```{r}
n_fun <- function(x){
  return(data.frame(y = 4, 
                    label = str_c("n = ", length(x))))
}

Ni_material <- df_matirial_test %>% 
  ggplot(aes(x = matirial_all, y = Ni, 
             color = matirial_all)) +
  stat_boxplot(geom = "errorbar", width = 0.2) +
  geom_boxplot(outlier.shape = NA) +
  # stat_summary(fun.data = n_fun, geom = "text") +
  stat_pvalue_manual(pwc, 
                     hide.ns = TRUE, 
                     remove.bracket = FALSE, tip.length = 0.0004,
                     y.position = 60, step.increase = 0.0015,
                     #label = "p = {scientific(p.adj, 2)}", label.size = 3
                     ) +
  # add the number of observations
  stat_summary(fun.data = n_fun, geom = "text", colour = "black") +
  # add mean point
  stat_summary(fun = mean, geom = "point", shape = 20, size = 5) +
  # add mean text
  stat_summary(fun.data = mean_fun, geom = "text", colour = "black",  
               position = position_nudge(x = 0.22)) +
  labs(x = "Building Material",
       y="Ni Concentration (mg/kg)",
       subtitle = get_test_label(res.kruskal, detailed = TRUE),
       caption = get_pwc_label(pwc)) +
  scale_y_continuous(# limits = quantile(df_newly_cleaned$Ni, c(0, 1)),
                     breaks = seq(0, 80, by = 10))+
  coord_cartesian(ylim = c(0, 80)) +
  theme(panel.border = element_blank(), 
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), 
        axis.line = element_line(colour = "black"),
        axis.text = element_text(colour = "black"),
        text=element_text(family="Helvetica"),
        legend.position = "none")
Ni_material
```


```{r}
ggsave("../fig_output/Material/Ni.png", Ni_material, width = 7, height = 5)
```

## Zn

```{r}
ggline(df_matirial_test, 
       x = "matirial_all", 
       y = "Zn", 
       add = c("mean_ci"), 
       xlab = "Building Material",
       font.tickslab = 12,
       ylab = "Zn Concentration (mg/kg)",
       title = "Mean Plot with 95% CI")
```

```{r}
res.kruskal <- df_matirial_test %>% 
  kruskal_test(Zn ~ matirial_all)
res.kruskal
```

```{r}
effect_size <- df_matirial_test %>% 
  kruskal_effsize(Zn ~ matirial_all)
effect_size
```

```{r}
pwc <-  df_matirial_test %>% 
  dunn_test(Zn ~ matirial_all, p.adjust.method = "bonferroni")
pwc
```



```{r}
n_fun <- function(x){
  return(data.frame(y = median(x) - 40, 
                    label = str_c("n = ", length(x))))
}

Zn_material <- df_matirial_test %>% 
  ggplot(aes(x = matirial_all, y = Zn, 
             color = matirial_all)) +
  stat_boxplot(geom = "errorbar", width = 0.2) +
  geom_boxplot(outlier.shape = NA) +
  # stat_summary(fun.data = n_fun, geom = "text") +
  stat_pvalue_manual(pwc, 
                     hide.ns = TRUE, 
                     remove.bracket = FALSE, tip.length = 0.0007,
                     y.position = 1650, step.increase = 0.0035,
                     #label = "p = {scientific(p.adj, 2)}", label.size = 3
                     ) +
  # add the number of observations
  stat_summary(fun.data = n_fun, geom = "text", colour = "black") +
  # add mean point
  stat_summary(fun = mean, geom = "point", shape = 20, size = 5) +
  # add mean text
  stat_summary(fun.data = mean_fun, geom = "text", colour = "black",  
               position = position_nudge(x = 0.22)) +
  labs(x = "Building Material",
       y="Zn Concentration (mg/kg)",
       subtitle = get_test_label(res.kruskal, detailed = TRUE),
       caption = get_pwc_label(pwc)) +
  scale_y_continuous(# limits = quantile(df_newly_cleaned$Zn, c(0, 1)),
                     breaks = seq(0, 2000, by = 200))+
  coord_cartesian(ylim = c(0, 2000)) +
  theme(panel.border = element_blank(), 
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), 
        axis.line = element_line(colour = "black"),
        axis.text = element_text(colour = "black"),
        text=element_text(family="Helvetica"),
        legend.position = "none")
Zn_material
```


```{r}
ggsave("../fig_output/Material/Zn.png", Zn_material, width = 7, height = 5)
```




```{r}
n_fun <- function(x){
  return(data.frame(y = 740, 
                    label = str_c("n = ", length(x))))
}

df_matirial_long %>%
  filter(matirial_contain != "no_structure") %>% 
  ggplot(aes(matirial_contain, Pb)) +
  stat_boxplot(geom = "errorbar", width = 0.2) +
  geom_boxplot(outlier.shape = NA,
               aes(fill = matirial_contain),
               show.legend = FALSE) +
  stat_summary(fun.data = n_fun, geom = "text") +
  labs(x = "Containing Building Matirials",
       y="Pb Concentration (mg/kg)") +
  scale_y_continuous(limits = quantile(df_matirial_long$Pb, c(0, 1)),
                     breaks = seq(0, 700, by = 100)) +
  coord_cartesian(ylim = c(0, 750)) +
  theme(panel.border = element_blank(), 
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), 
        axis.line = element_line(colour = "black"),
        axis.text = element_text(colour = "black", size = 10),
        text=element_text(family="Helvetica"))
```


# Timber House

```{r}
df_timber_samples <- df_matirial_test %>% 
  filter(matirial_all == "timber")

df_timber_homes <- df_timber_samples %>% 
  group_by(OwnerAddress) %>% 
  slice(n()) %>% 
  ungroup()
```

```{r}
df_timber_homes %>% 
  ggplot(aes(x = PropertyAge)) +
  geom_histogram(binwidth = 10, color = "white", boundary = 0) +
  labs(x = "Property Age (year)",
       y = "Number of Houses",
       title = "The total number of timber houses: 683") +
  scale_y_continuous(breaks = seq(0, 140, by = 20)) +
  scale_x_continuous(breaks = seq(0, 200, by = 10)) +
  # coord_cartesian(ylim = c(0, 1000)) +
  theme(panel.border = element_blank(), 
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), 
        axis.line = element_line(colour = "black"),
        axis.text = element_text(colour = "black"),
        text=element_text(family="Helvetica"),
        legend.position = "none")
```

```{r}
df_timber_homes %>% 
  filter(PropertyAge >= 50)

667/812
```

```{r}
df_timber_homes %>% 
  ggplot(aes(x = paint, fill = paint)) +
  geom_bar() +
  labs(x = "Painted or Unpainted",
       y = "Number of Houses",
       title = "The total number of timber houses: 683") +
  scale_y_continuous(breaks = seq(0, 600, by = 100))+
  #coord_cartesian(ylim = c(0, 1000)) +
  theme(panel.border = element_blank(), 
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), 
        axis.line = element_line(colour = "black"),
        axis.text = element_text(colour = "black"),
        text=element_text(family="Helvetica"),
        legend.position = "none")
```

```{r}
df_timber_homes %>% 
  count(paint)

668/812
```


```{r}
n_fun <- function(x){
  return(data.frame(y = median(x) + 30, 
                    label = str_c("n = ", length(x))))
}

mean_fun <- function(x){
  return(data.frame(y = mean(x),
                    label = format(round(mean(x, na.rm = TRUE), 1), nsmall = 1)
                    )
         )
}

df_timber %>% 
  ggplot(aes(x = paint, y = Pb, color = paint)) +
  stat_boxplot(geom = "errorbar", width = 0.2) +
  geom_boxplot(outlier.shape = NA) +
  # stat_summary(fun.data = n_fun, geom = "text") +
  stat_pvalue_manual(pwc, hide.ns = TRUE, remove.bracket = FALSE, 
                     tip.length = 0.001, y.position = 800, step.increase = 0.004) +
  # add the number of observations
  stat_summary(fun.data = n_fun, geom = "text", colour = "black") +
  # add mean point
  stat_summary(fun.y = mean, geom = "point", shape = 20, size = 7) +
  # add mean text
  stat_summary(fun.data = mean_fun, geom = "text", colour = "black",  
               position = position_nudge(x = 0.22)) +
  labs(x = "Building Material",
       y="Pb Concentration (mg/kg)",
       subtitle = get_test_label(res.kruskal, detailed = TRUE),
       caption = get_pwc_label(pwc)) +
  scale_y_continuous(limits = quantile(df_newly_cleaned$Pb, c(0, 1)),
                     breaks = seq(0, 1000, by = 100))+
  coord_cartesian(ylim = c(0, 1000)) +
  theme(panel.border = element_blank(), 
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), 
        axis.line = element_line(colour = "black"),
        axis.text = element_text(colour = "black"),
        text=element_text(family="Helvetica"),
        legend.position = "none")

ggsave("../fig_output/Material/Pb.png", width = 7, height = 5)
```


```{r eval=FALSE}
df_matirial_long <- pivot_longer(df_newly_cleaned,
                                 brick:no_structure,
                                 names_to = "matirial_name",
                                 values_to = "matirial_contain")

matirial_levels <- c("brick", "timber", "fibro", "metal", "stone", "no_structure")

df_matirial_test <- df_matirial_long %>%
  filter(!is.na(matirial_contain)) %>% 
  dplyr::select(- matirial_name) %>% 
  mutate(matirial_contain = factor(matirial_contain, levels = matirial_levels)) %>% 
  filter(matirial_contain != "no_structure")
```





