---
title: "Principal Component Analysis"
author: "Xiaochi"
date: "01/09/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(FactoMineR)
library(factoextra)
library(ggpubr)
```

Principal component analysis (PCA) allows us to summarize and to visualize the information in a data set containing observations described by multiple inter-correlated quantitative variables.
The information in a given data set corresponds to the total variation it contains. 
The goal of PCA is to identify directions (or principal components) along which the variation in the data is maximal.
In other words, PCA reduces the dimensionality of a multivariate data to two or three principal components, that can be visualized graphically, with minimal loss of information.

In our case, we have 8 trace elements concentration (As, Cd, Cr, Cu, Mn, Pb, Ni, Zn) of 17,256 samples from different regions of Australia. 
We can use PCA to reduce the number of variables needed to describe the variation between individual samples from different regions of Australia


# All Samples


```{r}
df_vege <- read_rds("../data_output/df_vege.rds")
res.pca <- PCA(df_vege[ , c("As", "Cd", "Cr", "Cu", "Mn", "Pb", "Ni", "Zn")], 
               graph = FALSE)
```

## Eigenvalues / Varianaces

The eigenvalues measure the amount of variation retained by each principal component (PC). 
Eigenvalues are large for the first PCs and small for the subsequent PCs.
That is, the first PC corresponds to the directions with the maximum amount of variation in the data set.

```{r}
eig.val <- get_eigenvalue(res.pca)
```


```{r}
fviz_eig(res.pca, addlabels = TRUE, title = "Scree Plot") +
  theme_classic2()
```

From the plot above, we observed that the PC1 (Dimension 1) and second PC2 (Dimension 2) together can explain 26.3% + 14.8% = 41.1% of the information (variances) contained in the data (all samples).

## Graph of individuals

Individual samples that are similar are grouped together on the plot.

Individuals plot with concentration ellipses:

```{r}
fviz_pca_ind(res.pca,
             geom.ind = "point", # show points only (but not "text")
             pointshape = 22,
             pointsize = 1,
             fill.ind = df_vege$ste_name,
             col.ind = df_vege$ste_name,
             alpha.ind = 0.5,
             palette = "Set1",
             addEllipses = TRUE, # Concentration ellipses
             #ellipse.type = "confidence",
             title = "Individuals Plot",
             legend.title = "State",
             mean.point = FALSE) +
  ggpubr::fill_palette("Set1") +
  theme_classic2()
```


Individuals plot with convex hulls:

```{r}
plot_individual_all <- fviz_pca_ind(res.pca,
             geom.ind = "point", # show points only (nbut not "text")
             pointshape = 22,
             pointsize = 1,
             fill.ind = df_vege$ste_name,
             col.ind = df_vege$ste_name,
             alpha.ind = 0.5,
             palette = "Set1",
             addEllipses = TRUE, # Concentration ellipses
             ellipse.type = "convex",
             title = "Individuals Plot",
             legend.title = "State",
             mean.point = FALSE) +
  ggpubr::fill_palette("Set1") +
  theme_classic2()

plot_individual_all
```


```{r}
df_vege %>% 
  count(ste_name, sort = TRUE)
```

## Graph of trace elements

```{r}
fviz_pca_var(res.pca, 
             col.var = "contrib",
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
             repel = TRUE,
             title = "Variable Correlation Plot",
             legend.title = "Trace element\ncontribution (%) to\nDim1 and Dim2") +
  theme_classic2()
```

The plot above is known as variable correlation plot.
The correlation between an original variable (trace element) and a principal component (Dim) is used as the coordinates on this plot.

The correlation plot contains much information. 
First, it shows the relationship between all 8 trace elements:

1. Positively correlated trace elements are grouped together (e.g. Zn and Pb);

2. Negatively correlated trace elements are positioned on opposite sides of the plot origin (opposed quadrants);

Second, the length of the arrow indicates how much the PC1 and PC2 (Dim1 and Dim2) can represent the original trace elements,in other word, the quality of the representation:

1. The closer a trace element is to the circumference of the circle (e.g. Zn), the better its representation by PC1 and PC2.

2. The closer a trace element is to the centre of the circle (e.g. Ni), the fewer its representation by the PC1 and PC2.

Third, the colour of the arrow shows the importance of the trace element, (i.e. the total contribution of the trace element to PC1 and PC2). 


# Samples from Sydney, Melbourne, and Brisbane

```{r}
df_3cities <- df_vege %>% 
  filter(sua_name %in% c("Sydney", "Melbourne", "Brisbane"))

res.pca.3cities <- PCA(df_3cities[ , c("As", "Cd", "Cr", "Cu", "Mn", "Pb", "Ni", "Zn")], 
                       graph = FALSE)
```

## Eigenvalues / Varianaces

```{r}
fviz_eig(res.pca.3cities, addlabels = TRUE, title = "Scree Plot") +
  theme_classic2()
```

## Graph of individuals

```{r}
fviz_pca_ind(res.pca.3cities,
             axes = c(1, 2),
             geom.ind = "point", # show points only (nbut not "text")
             pointshape = 22,
             pointsize = 1,
             fill.ind = df_3cities$sua_name,
             col.ind = df_3cities$sua_name,
             alpha.ind = 0.5,
             palette = "Set1",
             addEllipses = TRUE, # Concentration ellipses
             #ellipse.type = "convex",
             title = "Individuals Plot",
             legend.title = "Cities",
             mean.point = FALSE) +
  ggpubr::fill_palette("Set1") +
  theme_classic2()
```


```{r}
plot_individual_3cities <- fviz_pca_ind(res.pca.3cities,
             geom.ind = "point", # show points only (nbut not "text")
             pointshape = 22,
             pointsize = 1,
             fill.ind = df_3cities$sua_name,
             col.ind = df_3cities$sua_name,
             alpha.ind = 0.5,
             palette = "Set1",
             addEllipses = TRUE, # Concentration ellipses
             ellipse.type = "convex",
             title = "Individuals Plot",
             legend.title = "Cities",
             mean.point = FALSE) +
  ggpubr::fill_palette("Set1") +
  theme_classic2()

plot_individual_3cities
```


```{r}
df_3cities %>% 
  count(sua_name, sort = TRUE)
```

## Graph of trace elements

```{r}
fviz_pca_var(res.pca.3cities, 
             col.var = "contrib",
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
             repel = TRUE,
             title = "Variable Correlation Plot",
             legend.title = "Trace element\ncontribution (%) to\nDim1 and Dim2"
             ) +
  theme_classic2()
```

The plot above shows that in the samples of 3 cities:

1. Pb, Zn, As, Cu grouped together thus they were correlated positively;

2. Mn, Ni, Cr grouped together thus they were correlated positively;

3. Pb, Zn, As, Cu, Cd were positively correlated with PC1 while negatively correlated with PC2;

4. Mn, Ni, and Cr were positively correlated both with PC1 and PC2;

5. Pb and Zn can be well represented by PC1 and PC2;

6. Pb and Zn were the most important trace elements in PC1 and PC2



