---
title: "Untitled"
author: "Xiaochi"
date: "21/11/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(DT)
library(tidyverse)
library(skimr)
library(asbio)
```

```{r Data Import}
df_vege <- read_rds("../data_output/df_vege.rds")
names(df_vege)
df_vege %>% 
  count(OwnerAddress)
```

```{r}
df_vege %>% 
  select(As, Cd, Cr, Cu, Mn, Ni, Pb, Zn) %>% 
  skim()
```

```{r median_cl_boot}
median_cl_boot <- function(x, conf = 0.95) {
    lconf <- (1 - conf)/2
    uconf <- 1 - lconf
    require(boot)
    bmedian <- function(x, ind) median(x[ind])
    bt <- boot(x, bmedian, 1000)
    bb <- boot.ci(bt, type = "perc")
    data.frame(y = median(x), ymin = quantile(bt$t, lconf), ymax = quantile(bt$t, 
        uconf))
}
```


```{r df_long summary}
df_long <- df_vege %>% 
  pivot_longer(cols = As : Zn,
               names_to = "element",
               values_to = "concentration")
```

```{r}
# n > LoQ
df_vege %>% 
  filter(Zn > 1)
```



```{r df_long summary}
df_long %>% 
  group_by(element) %>% 
  summarise(
    min = min(concentration),
    percentile_5 = quantile(concentration, 0.05),
    median = median(concentration),
    percentile_95 = quantile(concentration, 0.95),
    max = max(concentration)
  )
```

```{r df_newly_cleaned summary}
As_guide <- 100
Cd_guide <- 20
Cr_guide <- 100
Cu_guide <- 6000
Pb_guide <- 300
Mn_guide <- 3800
Ni_guide <- 400
Zn_guide <- 7400
```


```{r}
mean_cl_boot(df_vege$As)
```



```{r df_newly_cleaned summary}
# homes with a sample > guidelines
n_homes <- df_vege %>% 
  filter(Ni > Ni_guide) %>% 
  count(OwnerAddress) %>% 
  nrow()

n_homes
n_homes/3609*100
```


```{r df_newly_cleaned summary}
# smaples > guidelines
n_samples <- df_vege %>% 
  filter(Zn > Zn_guide) %>% 
  nrow()

n_samples  
n_samples/17256*100
```


# 3 cities

```{r}
library(ggpubr)
```


```{r}
df_3cities <- read_rds("../data_output/df_3cities.rds")
As_guide <- 100
Cd_guide <- 20
Cr_guide <- 100
Cu_guide <- 6000
Pb_guide <- 300
Mn_guide <- 3800
Ni_guide <- 400
Zn_guide <- 7400
```


```{r}
mean_fun <- function(x){
  return(data.frame(y = mean(x),
                    label = format(round(mean(x, na.rm = TRUE), 1), nsmall = 1)))
}

ci_fun <- function(x){
  return(data.frame(y = mean_cl_boot(x),
                    label = format(round(mean(x, na.rm = TRUE), 1), nsmall = 1)))
}


```

## As

```{r}
plot_As <- df_3cities %>% 
  mutate(sua_name = factor(sua_name, levels = c("Sydney", "Melbourne", "Brisbane"))) %>% 
  ggplot(aes(x = sua_name, y = As)) +
  #stat_regline_equation() +
  #geom_hline(aes(yintercept = As_guide), linetype = "dashed", size = 1, colour = "black") +
  # mean
  stat_summary(fun = mean, geom = "point", size = 3, aes(colour = sua_name)) +
  stat_summary(fun.data = mean_fun, geom = "text", colour = "black", position = position_nudge(x = 0.2)) +
  # confidence interval
  stat_summary(fun.data = mean_cl_boot, geom = "errorbar", aes(colour = sua_name)) +
  labs(x = "Cities") +
  theme_pubr() +
  theme(legend.position = "none")
plot_As
```

## Cd_guide <- 20

```{r}
plot_Cd <- df_3cities %>% 
  mutate(sua_name = factor(sua_name, levels = c("Sydney", "Melbourne", "Brisbane"))) %>% 
  ggplot(aes(x = sua_name, y = Cd)) +
  #stat_regline_equation() +
  #geom_hline(aes(yintercept = Pb_guide), linetype = "dashed", size = 1, colour = "black") +
  # mean
  stat_summary(fun = mean, geom = "point", size = 3, aes(colour = sua_name)) +
  stat_summary(fun.data = mean_fun, geom = "text", colour = "black", position = position_nudge(x = 0.2)) +
  # confidence interval
  stat_summary(fun.data = mean_cl_boot, geom = "errorbar", aes(colour = sua_name)) +
  labs(x = "Cities") +
  theme_pubr() +
  theme(legend.position = "none")

plot_Cd
```


## Cr_guide <- 100

```{r}
plot_Cr <- df_3cities %>% 
  mutate(sua_name = factor(sua_name, levels = c("Sydney", "Melbourne", "Brisbane"))) %>% 
  ggplot(aes(x = sua_name, y = Cr)) +
  #stat_regline_equation() +
  geom_hline(aes(yintercept = Cr_guide), linetype = "dashed", size = 1, colour = "black") +
  # mean
  stat_summary(fun = mean, geom = "point", size = 3, aes(colour = sua_name)) +
  stat_summary(fun.data = mean_fun, geom = "text", colour = "black", position = position_nudge(x = 0.2)) +
  # confidence interval
  stat_summary(fun.data = mean_cl_boot, geom = "errorbar", aes(colour = sua_name)) +
  scale_y_continuous(breaks = seq(40, 100, 10)) +
  labs(x = "Cities") +
  theme_pubr() +
  theme(legend.position = "none")

plot_Cr
```


## Cu_guide <- 6000

```{r}
plot_Cu <- df_3cities %>% 
  mutate(sua_name = factor(sua_name, levels = c("Sydney", "Melbourne", "Brisbane"))) %>% 
  ggplot(aes(x = sua_name, y = Cu)) +
  #stat_regline_equation() +
  #geom_hline(aes(yintercept = Pb_guide), linetype = "dashed", size = 1, colour = "black") +
  # mean
  stat_summary(fun = mean, geom = "point", size = 3, aes(colour = sua_name)) +
  stat_summary(fun.data = mean_fun, geom = "text", colour = "black", position = position_nudge(x = 0.2)) +
  # confidence interval
  stat_summary(fun.data = mean_cl_boot, geom = "errorbar", aes(colour = sua_name)) +
  labs(x = "Cities") +
  theme_pubr() +
  theme(legend.position = "none")

plot_Cu
```



## Pb_guide <- 300

```{r}
plot_Pb <- df_3cities %>% 
  mutate(sua_name = factor(sua_name, levels = c("Sydney", "Melbourne", "Brisbane"))) %>% 
  ggplot(aes(x = sua_name, y = Pb)) +
  #stat_regline_equation() +
  geom_hline(aes(yintercept = Pb_guide), linetype = "dashed", size = 1, colour = "black") +
  # mean
  stat_summary(fun = mean, geom = "point", size = 3, aes(colour = sua_name)) +
  stat_summary(fun.data = mean_fun, geom = "text", colour = "black", position = position_nudge(x = 0.2)) +
  # confidence interval
  stat_summary(fun.data = mean_cl_boot, geom = "errorbar", aes(colour = sua_name)) +
  labs(x = "Cities") +
  theme_pubr() +
  theme(legend.position = "none")

plot_Pb
```


## Mn_guide <- 3800

```{r}
plot_Mn <- df_3cities %>% 
  mutate(sua_name = factor(sua_name, levels = c("Sydney", "Melbourne", "Brisbane"))) %>% 
  ggplot(aes(x = sua_name, y = Mn)) +
  #stat_regline_equation() +
  #geom_hline(aes(yintercept = Pb_guide), linetype = "dashed", size = 1, colour = "black") +
  # mean
  stat_summary(fun = mean, geom = "point", size = 3, aes(colour = sua_name)) +
  stat_summary(fun.data = mean_fun, geom = "text", colour = "black", position = position_nudge(x = 0.2)) +
  # confidence interval
  stat_summary(fun.data = mean_cl_boot, geom = "errorbar", aes(colour = sua_name)) +
  labs(x = "Cities") +
  theme_pubr() +
  theme(legend.position = "none")

plot_Mn
```



## Ni_guide <- 400

```{r}
plot_Ni <- df_3cities %>% 
  mutate(sua_name = factor(sua_name, levels = c("Sydney", "Melbourne", "Brisbane"))) %>% 
  ggplot(aes(x = sua_name, y = Ni)) +
  #stat_regline_equation() +
  #geom_hline(aes(yintercept = Pb_guide), linetype = "dashed", size = 1, colour = "black") +
  # mean
  stat_summary(fun = mean, geom = "point", size = 3, aes(colour = sua_name)) +
  stat_summary(fun.data = mean_fun, geom = "text", colour = "black", position = position_nudge(x = 0.2)) +
  # confidence interval
  stat_summary(fun.data = mean_cl_boot, geom = "errorbar", aes(colour = sua_name)) +
  labs(x = "Cities") +
  theme_pubr() +
  theme(legend.position = "none")

plot_Ni
```



## Zn_guide <- 7400

```{r}
plot_Zn <- df_3cities %>% 
  mutate(sua_name = factor(sua_name, levels = c("Sydney", "Melbourne", "Brisbane"))) %>% 
  ggplot(aes(x = sua_name, y = Zn)) +
  #stat_regline_equation() +
  #geom_hline(aes(yintercept = Pb_guide), linetype = "dashed", size = 1, colour = "black") +
  # mean
  stat_summary(fun = mean, geom = "point", size = 3, aes(colour = sua_name)) +
  stat_summary(fun.data = mean_fun, geom = "text", colour = "black", position = position_nudge(x = 0.2)) +
  # confidence interval
  stat_summary(fun.data = mean_cl_boot, geom = "errorbar", aes(colour = sua_name)) +
  labs(x = "Cities") +
  theme_pubr() +
  theme(legend.position = "none")

plot_Zn
```

```{r fig.width=10, fig.height=5}
ggarrange(plot_As, plot_Cd, plot_Cr, plot_Cu,
          plot_Pb, plot_Mn, plot_Ni, plot_Zn,
          ncol = 4, nrow = 2)
```


# go

```{r}
#+++++++++++++++++++++++++
# Function to calculate the mean and the standard deviation
  # for each group
#+++++++++++++++++++++++++
# data : a data frame
# varname : the name of a column containing the variable to be summarized
# groupnames : vector of column names to be used as grouping variables

data_summary <- function(data, varname, groupnames){
  require(plyr)
  summary_func <- function(x, col){
    c(mean = mean(x[[col]], na.rm=TRUE),
      sd = sd(x[[col]], na.rm=TRUE))
  }
  
  summary_func <- mean_cl_boot(df_3cities, Pb)
  
  data_sum <- ddply(data, groupnames, .fun=summary_func, varname)
  data_sum <- rename(data_sum, c("mean" = varname))
 return(data_sum)
}


library(ggpubr)
```


```{r}
df_3cities %>% 
  mutate(sua_name = factor(sua_name, levels = c("Sydney", "Melbourne", "Brisbane"))) %>% 
  ggplot(aes(x = sua_name, y = Pb)) +
  stat_summary(fun.y = mean, geom = "point", size = 3, aes(colour = sua_name)) +
  stat_summary(fun.data = mean_cl_boot, geom = "errorbar", aes(colour = sua_name))+
  theme_pubr() +
  theme(legend.position = "none")
```


```{r}
```


```{r}
df_3cities %>%
  group_by(sua_name) %>% 
  mean_cl_boot(Pb)

mean_cl_boot(df_3cities$Pb)

df_3cities %>% 
  
```



```{r}
library(Hmisc)

df_3cities %>% 
  group_by(sua_name) %>% 
  select(Pb) %>% 
  smean.cl.boot

df_3cities %>% 
  group_by(sua_name) %>% 
  select(Pb) %>% 
  smean.cl.boot
  
  

mean_cl_boot(df_3cities$Pb)

smean.cl.boot(df_3cities$Pb)
levels(df_3cities$sua_name)
```

